The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-02 src/ms.tex
Update src/ms.tex
Co-authored-by: P. L. Lim <2090236+pllim@users.noreply.github.com>

\begin{description}
  \item[Supporting an active group of maintainers] With funding, can pay maintainers. But: time commitment, some positions don't allow. Need for new career paths on the spectrum from software engineer to astronomy researcher. Also need to attract new non-hired contributors to sustain the project, but challenging when the code has become quite complex (astropy as an "institution", don't want to be a walled-off group). (Need for fast feedback and code reviews to empower contributors, but puts a burden on maintainers)
  \item[Long-term / sustained funding for maintaining infrastructure] Further from "science," still critical to astropy, but who will provide updates and maintenance? More than just updating versions and releasing. (grants last 3 years; infrastructure evolves, nature of open source ecosystem)
  \item[Understanding, communicating with, and engaging our user communities] Different overlapping and intersecting communities of users: telescopes, archives, researchers, students, educators, general public. Communities have different needs from Astropy. Also, as ecosystem grows, making sure users know about all of the functionality (workshops, tutorials, educational materials, discoverability, accessibility) (Continued engagement with user community).
\end{description}

>>>>

\begin{description}
  \item[Supporting an active group of maintainers] With funding, can pay maintainers. But: time commitment, some positions don't allow. Need for new career paths on the spectrum from software engineer to astronomy researcher. Also need to attract new non-hired contributors to sustain the project, but challenging when the code has become quite complex (astropy as an "institution", don't want to be a walled-off group). (Need for fast feedback and code reviews to empower contributors, but puts a burden on maintainers)
  \item[Diversity of contributor, maintainer, coordinator communities] Practical issues: translation of content and documentation, github is not accessible in some countries.
  \item[Long-term / sustained funding for maintaining infrastructure] Software and packaging infrastructure
  includes but not limited to Continuous Integration (CI), test plugins, documentation builds, and package
  delivery. Keeping the infrastructure working is essential in software development and operations.
  This kind of work has low visibility and is not attractive to scientists or volunteer contributors;
  therefore, it is most effective to delegate such tasks to paid roles. \astropy secured a three-year grant
  for this but the situation remains uncertain once the grant runs out, as infrastructure evolves and
  requires constant maintenance and upgrades. Some of the engineers currently in these roles are
  also employees of research institutions that may leave the Project without much notice, adding to
  the uncertainty factor.
  \item[Understanding, communicating with, and engaging our user communities] Different overlapping and intersecting communities of users: telescopes, archives, researchers, students, educators, general public. Communities have different needs from Astropy. Also, as ecosystem grows, making sure users know about all of the functionality (workshops, tutorials, educational materials, discoverability, accessibility) (Continued engagement with user community).
\end{description}
